The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-24 Background/ruby.tex
fixed references and spacing

This is a test e-mail message.
"""
# construct a post request with email set to attack_string
# attack_string => sai@example.com%0abcc:spc@example.com%0aSubject:Hello
Net::SMTP.start('localhost', 1025) do |smtp|
smtp.send_message message, 'sch@example.com',
'to@todomain.com'
end
# Headers get added, and Subject field changes to what we set.
end
\end{lstlisting}

>>>>

This is a test e-mail message.
"""
# construct a post request with email set to attack_string
# attack_string => s@example.com%0abcc:spc@example.com%0aSubject:Hello
Net::SMTP.start('localhost', 1025) do |smtp|
smtp.send_message message, 'sch@example.com',
'to@todomain.com'
end
# Headers get added, and Subject field changes to what we set.
end
\end{lstlisting}

### 2016-05-24 abstract.tex
fixed references and spacing

	This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web. Using a black-box testing approach, the system crawled \urls URLs identify web pages which contained form fields. \forms such forms were found by the system, of which \emailforms forms contained \email fields. We then tested \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email. Of these \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains. Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on well-known spamming blacklists. This work shows that \ehi vulnerabilities are widespread and deserve future research attention.
\end{abstract}

>>>>

	This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web. Using a black-box testing approach, the system crawled \urls URLs to identify web pages which contained form fields. \forms such forms were found by the system, of which \emailforms forms contained \email fields. We then tested \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email. Of these, \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains. Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spamming blacklists. This work shows that \ehi vulnerabilities are widespread and deserve future research attention.
\end{abstract}
